Confirmation of \srcfull{} as a long period radio transient

### 2025-05-29 paper/main.tex
Updated everything on account of two new ATCA detections. Plots updated, ephemeris updated, scripts updated, paper updated.

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[S. J. McSweeney et al.]{
Samuel J. McSweeney$^{1}$,
Natasha Hurley-Walker$^{1}$,
Csan\'{a}d Horv\'{a}th$^{1}$,
Akash Anumarlapudi$^{2}$,
\newauthor
Angie Waszewski$^{1}$,
Dougal Dobie$^{3,4}$,
John Morgan$^{1}$,
David L.~Kaplan$^{2}$,
and Ziteng Wang$^{1}$
\\
% List of institutions
$^{1}$International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia\\
$^{4}$Department of Physics, University of Wisconsin-Milwaukee, P.O. Box 413, Milwaukee, WI 53201, USA\\
$^{2}$Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia\\
$^{3}$ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav), Hawthorn, VIC 3122, Australia
}

@@

Pulses from \src{} were detected with the Murchison Widefield Array \citep[MWA;][]{Tingay2013}, the Australian SKA Pathfinder \citep[ASKAP;][]{2021PASA...38....9H} and MeerKAT \citep{2016mks..confE...1J}, are all radio interferometers capable of imaging.
A summary of all the observations included in this work is summarised in \Tab~\ref{tbl:obs}.
In this section, we describe how each telescope was used to generate dynamic spectra of \src{}.

\begin{table*}
  \centering
  \caption{Observations summary}
  \label{tbl:obs}
  \begin{tabular}{lllcccc}
    \hline
    Date range & Telescope & Project & $\nu$ & $\Delta\nu$ & Obs. length & Number of \\ 
    (MJD) & & & (MHz) & (MHz) & (min) & pulses \\
    \hline 
    59965 & ASKAP & SB47253 (original discovery) & 887.5 & 288 & 12.1 & 1 \\
    59966 & MWA & G0060 & 161.92 & 15.36 & 6.7 & 1 \\
    %60084 & MWA & G0057 & 154.24 & 30.72 & N/A & $\le$ 1 \\
    60040  & ASKAP & SB49153 & 887.5 & 288 & 12.1 & 1 \\
    60092 - 60093 & MeerKAT & DDT-20230525-DD-01 & 1284 & 856 & 307 & 4 \\
    60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & (Each obs.) 4.9 & 16 \\
    60503 & ASKAP & SB63600 & 887.5 & 288 & 12.3 & 1 \\
    60572 & MWA & D0042 & 184.96 & 30.72 & (Each obs.) 4.9 & 4 \\
    60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & (Each obs.) 4.9 & 17 \\
    60602 & MeerKAT & DDT-20241015-NH-01 & 812.8 & 495.3 & 10 & 1 \\
    \hline
  \end{tabular}
\end{table*}

@@

% ** ANGIE **
% Plz add a short paragraph here with the essential details of the IPS observation included in this paper: G0060, upper half-band only, how the images were made. I'll (SM) add a few sentences about how I selected that observation in the first place.
An additional MWA observation made as part of the MWA Interplanetary Scintillation (IPS) Survey, project code G0060, has also been included in this present study. 
A full description of how MWA IPS observations are scheduled and processed can be found in Section~2 of \citet{Morgan2022}.
Details of the imaging of IPS observations since the first data release can be found in Waszewski et al. (submitted).
The two adjacent 200-second observations included in this work are a sub-section of a full 10-minute near-Sun observation (30$^{\circ}$ elongation).
These observations are taken over two equal bands of frequency, centred on approximately 80\,MHz and 160\,MHz. For this study, only the upper band has been processed. 
The observation was self-calibrated against a sky model based on the GLEAM survey \citep{Hurley-Walker2017} using \textsc{mwa\_hyperdrive}\footnote{\url{https://github.com/MWATelescope/mwa_hyperdrive}}, and then imaged using \textsc{WSClean}.
\src{} is clearly visible as a point source in the image, and the lightcurve presented in this work is the result of averaging over the 15.36-MHz subband, using 10-second time bins.

@@

@@

\begin{table}
  \centering
  \caption{Timing ephemeris for \src{}}
  \label{tbl:ephemeris}
  \begin{tabular}{lc}
    \hline
    Parameter & Value \\
    \hline
    Period (s) & $4186.3283 \pm 0.0003$ \\
    PEPOCH (MJD) & $59965.03791 \pm 0.00003$ \\
    DM (pc/cm$^{-3}$) & $763 \pm 25$ \\
    $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$ \\
    \hline
  \end{tabular}
\end{table}

@@

The measured DM of $763 \pm 25\,{\rm pc}\,{\rm cm}^{-3}$ is slightly higher than, but still consistent with, the in-band measurement of $710^{+200}_{-180}\,{\rm pc}\,{\rm cm}^{-3}$ given in \citetalias{2024MNRAS.535..909D}.
Because we have not attempted to simultaneously fit for both DM and scattering timescale, there will remain some small systematic error on this reported DM measurement.
Note, in particular, that the YMW16 and NE2001 models predict a slightly longer scattering time scale than the $70\,$ms that we have assumed throughout this work.
Breaking the degeneracy is possible in principle with a higher S/N average profile than what is achievable with the current data set.

@@

No significant linear or circular polarised emission was detected in the 2023 MeerKAT pulses.
This is likely due to low S/N coupled with the source not being centred in the beam.
Much more careful imaging analysis would be needed to obtain reliable measurements or limits on the polarised components of those pulses.

@@

@@

 This scientific work uses data obtained from Inyarrimanha Ilgari Bundara, the CSIRO Murchison Radio-astronomy Observatory. Support for the operation of the MWA is provided by the Australian Government (NCRIS), under a contract to Curtin University administered by Astronomy Australia Limited. ASVO has received funding from the Australian Commonwealth Government through the National eResearch Collaboration Tools and Resources (NeCTAR) Project, the Australian National Data Service (ANDS), and the National Collaborative Research Infrastructure Strategy.
% Skipped because it is acknowledged below.
% We acknowledge the Pawsey Supercomputing Centre which is supported by the Western Australian and Australian Governments.
% ASKAP -- I have fixed this to use the correct name for the observatory
The Australian SKA Pathfinder is part of the Australia Telescope National Facility which is managed by CSIRO. Operation of ASKAP is funded by the Australian Government with support from the National Collaborative Research Infrastructure Strategy. ASKAP and the MWA use the resources of the Pawsey Supercomputing Centre. Establishment of ASKAP, Inyarrimanha Ilgari Bundara, and the Pawsey Supercomputing Centre are initiatives of the Australian Government, with support from the Government of Western Australia and the Science and Industry Endowment Fund. We acknowledge the Wajarri Yamaji People as the Traditional Owners and Native Title Holders of the observatory site.

@@

It can be shown that pulses scatter-broadened by a thin screen\footnote{Relaxing the assumption of a single, thin, isotropic screen could affect the shape of the scattered pulse in ways that could plausibly affect timing \citep{2009MNRAS.395.1391R}, but quantification of this is beyond the scope of this appendix.} will appear to the observer as the original pulse convolved with a one-sided exponential kernel with an associated timescale $\tau$ \citep{1972MNRAS.157...55W,1973MNRAS.163..345W}.
For intrinsically Gaussian pulses of scale $\sigma$, the result of this convolution is well described by the \textit{exponentially modified Gaussian} (EMG), as given in \Eqn~\ref{eqn:emg}.

@@

\begin{table*}
  \centering
  \caption{Times of arrival and other fitted pulse properties}
  \label{tbl:toas}
  \begin{tabular}{cccccc}
\hline
Telescope & Freq & ToA & $S_{\rm peak}$ & $\sigma$ & Fluence \\
 & (MHz) & (MJD) & (Jy) & (s) & (Jy\,s) \\
\hline
ASKAP & 888 & 59965.0429346(42) & 0.184(5) & 29.1(4) & 13.4(2) \\
MWA & 170 & 59966.061584(40) & 4(1) & 40(7) & 358(55) \\
ASKAP & 888 & 60040.913447(32) & 0.015(3) & 25(3) & 1.0(1) \\
MeerKAT & 1284 & 60092.8995476(100) & 0.0032(4) & 12.8(9) & 0.104(7) \\
MeerKAT & 1284 & 60092.947966(10) & 0.0033(6) & 12(1) & 0.10(1) \\
MeerKAT & 1284 & 60092.996466(11) & 0.0032(3) & 15.8(9) & 0.125(7) \\
MeerKAT & 1284 & 60093.044919(12) & 0.0030(3) & 16(1) & 0.122(7) \\
MWA & 200 & 60481.637466(65) & 0.8(4) & 24(8) & 50(11) \\
MWA & 200 & 60485.658977(33) & 0.7(2) & 16(4) & 29(3) \\
MWA & 200 & 60489.632266(20) & 1.4(3) & 14(2) & 48(3) \\
MWA & 200 & 60492.588020(24) & 2.4(6) & 14(3) & 87(7) \\
MWA & 200 & 60496.609639(18) & 1.5(3) & 17(2) & 67(4) \\
MWA & 200 & 60503.587085(14) & 2.0(2) & 17(2) & 82(3) \\
ASKAP & 888 & 60503.6347610(51) & 0.151(7) & 16.4(5) & 6.2(2) \\
MWA & 200 & 60506.542809(33) & 2(1) & 9(4) & 57(7) \\
MWA & 200 & 60510.564531(11) & 2.0(2) & 16(1) & 79(3) \\
MWA & 200 & 60519.528813(29) & 2.4(8) & 14(4) & 86(10) \\
MWA & 200 & 60522.533028(16) & 1.6(2) & 18(2) & 76(3) \\
MWA & 200 & 60527.524033(14) & 1.8(2) & 16(2) & 73(3) \\
MWA & 200 & 60530.528339(16) & 1.6(2) & 17(2) & 68(4) \\
MWA & 200 & 60537.506042(13) & 2.1(3) & 17(2) & 92(4) \\
MWA & 200 & 60541.479447(47) & 1.1(5) & 14(5) & 41(6) \\
MWA & 200 & 60544.483761(15) & 1.6(2) & 20(2) & 79(3) \\
MWA & 200 & 60551.461625(16) & 2.2(3) & 16(2) & 85(4) \\
MWA & 185 & 60572.395455(15) & 1.9(3) & 15(2) & 74(3) \\
MWA & 185 & 60572.443943(21) & 1.8(3) & 16(2) & 73(4) \\
MWA & 185 & 60572.540824(18) & 1.6(3) & 16(2) & 64(4) \\
MWA & 185 & 60572.589281(31) & 1.6(4) & 21(4) & 82(8) \\
MWA & 200 & 60592.456765(27) & 0.7(2) & 19(3) & 34(3) \\
MWA & 200 & 60592.505159(33) & 0.7(2) & 19(4) & 35(4) \\
MWA & 200 & 60593.474369(26) & 0.8(2) & 15(3) & 29(3) \\
MWA & 200 & 60593.522901(46) & 0.6(2) & 19(5) & 27(4) \\
MWA & 200 & 60594.443484(21) & 0.9(2) & 18(2) & 43(3) \\
MWA & 200 & 60594.491990(33) & 0.6(3) & 12(4) & 19(2) \\
MWA & 200 & 60595.461118(29) & 0.7(2) & 19(3) & 33(3) \\
MWA & 200 & 60595.509617(25) & 0.8(2) & 13(3) & 27(2) \\
MWA & 200 & 60596.430283(20) & 1.0(2) & 16(2) & 39(3) \\
MWA & 200 & 60596.478721(23) & 0.9(2) & 17(3) & 39(3) \\
MWA & 200 & 60597.447846(41) & 0.5(2) & 16(5) & 22(3) \\
MWA & 200 & 60597.496319(30) & 0.8(2) & 19(3) & 38(4) \\
MWA & 200 & 60599.434635(17) & 1.2(2) & 13(2) & 39(2) \\
MWA & 200 & 60599.483122(24) & 1.0(3) & 13(3) & 32(3) \\
MWA & 200 & 60600.500655(31) & 0.7(2) & 16(4) & 30(3) \\
MWA & 200 & 60602.438964(32) & 0.7(2) & 21(4) & 36(4) \\
MWA & 200 & 60602.487394(27) & 0.8(2) & 20(3) & 39(3) \\
MeerKAT & 813 & 60602.5835733(40) & 0.044(2) & 14.9(4) & 1.64(4) \\
\hline
  \end{tabular}
\end{table*}

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[S. J. McSweeney et al.]{
Samuel J. McSweeney$^{1}$,
Natasha Hurley-Walker$^{1}$,
Csan\'{a}d Horv\'{a}th$^{1}$,
Akash Anumarlapudi$^{2}$,
\newauthor
Angie Waszewski$^{1}$,
Dougal Dobie$^{3,4}$,
David L.~Kaplan$^{2}$,
John Morgan$^{5}$,
and Ziteng Wang$^{1}$
\\
% List of institutions
$^{1}$International Centre for Radio Astronomy Research, Curtin University, Bentley, WA 6102, Australia\\
$^{2}$Sydney Institute for Astronomy, School of Physics, The University of Sydney, NSW 2006, Australia\\
$^{3}$ARC Centre of Excellence for Gravitational Wave Discovery (OzGrav), Hawthorn, VIC 3122, Australia\\
$^{4}$Department of Physics, University of Wisconsin-Milwaukee, P.O. Box 413, Milwaukee, WI 53201, USA\\
$^{5}$CSIRO Space and Astronomy, P.O. Box 1130, Bentley, WA 6102, Australia\\
}

@@

Pulses from \src{} were detected with the Murchison Widefield Array \citep[MWA;][]{Tingay2013}, the Australian SKA Pathfinder \citep[ASKAP;][]{2021PASA...38....9H}, MeerKAT \citep{2016mks..confE...1J}, and the Australia Telescope Compact Array (ATCA, \todo{CITATION??}), all radio interferometers capable of imaging.
A summary of all the observations containing pulse detections included in this work is summarised in \Tab~\ref{tbl:obs}.
In this section, we describe how each telescope was used to generate dynamic spectra of \src{}.

\begin{table*}
  \centering
  \caption{Observations summary}
  \label{tbl:obs}
  \begin{tabular}{lllcccc}
    \hline
    Date range & Telescope & Project & $\nu$ & $\Delta\nu$ & Obs. (num. $\times$) & Number of \\ 
    (MJD) & & & (MHz) & (MHz) & length (min) & pulses \\
    \hline 
    59965 & ASKAP & SB47253 (original discovery) & 887.5 & 288 & 12.1 & 1 \\
    59966 & MWA & G0060 & 161.92 & 15.36 & 6.7 & 1 \\
    %60084 & MWA & G0057 & 154.24 & 30.72 & N/A & $\le$ 1 \\
    60040  & ASKAP & SB49153 & 887.5 & 288 & 12.1 & 1 \\
    60092 - 60093 & MeerKAT & DDT-20230525-DD-01 & 1284 & 856 & 307 & 4 \\
    60463 - 60563 & MWA & G0080 & 200.32 & 30.72 & $16 \times 4.9$ & 16 \\
    60503 & ASKAP & SB63600 & 887.5 & 288 & 12.3 & 1 \\
    60572 & MWA & D0042 & 184.96 & 30.72 & $4 \times 4.9$ & 4 \\
    60587 & ATCA & \todo{?????} & 2100 & 2048 & 93.2 & 2 \\
    60592 - 60602 & MWA & D0042 & 200.32 & 30.72 & $17 \times 4.9$ & 17 \\
    60602 & MeerKAT & DDT-20241015-NH-01 & 812.8 & 495.3 & 10 & 1 \\
    \hline
  \end{tabular}
\end{table*}

@@

An additional MWA observation made as part of the MWA Interplanetary Scintillation (IPS) Survey, project code G0060, taken just one day after the original ASKAP pulse, was found to have \src{} in the field of view.
The pulse was detected as a point source in the image formed from the third of three adjacent 200-second, near-Sun observations (30$^{\circ}$ elongation).
In this paper we present both the second and third observations (6.7 minutes total), in order to make the contrast between detection and non-detection more visible in the lightcurve formed by averaging over the 15.36-MHz subband, using 10-second time bins.
A full description of how MWA IPS observations are scheduled and processed can be found in Section~2 of \citet{Morgan2022}, but the essential details are summarised here.
The observations are taken over two equal bands of frequency, centred on approximately 80\,MHz and 160\,MHz.
For this study, only the upper band has been processed. 
The observations were self-calibrated against a sky model based on the GLEAM survey \citep{Hurley-Walker2017} using \textsc{mwa\_hyperdrive}\footnote{\url{https://github.com/MWATelescope/mwa_hyperdrive}}, and then imaged using \textsc{WSClean}.
Further details of the imaging of IPS observations since the first data release can be found in Waszewski et al. (submitted).

@@

\subsection{ATCA}

\todo{Akash to add some paragraphs here with details of processing ATCA data:}
\begin{itemize}
    \item Describe both Oct 4 and Oct 12 observations
    \item Mention that the Oct 12 observations did not yield any detections (even though there were four chances for it to do so!).
\end{itemize}

@@

\begin{table}
  \centering
  \caption{Timing ephemeris for \src{}}
  \label{tbl:ephemeris}
  \begin{tabular}{lc}
    \hline
    Parameter & Value \\
    \hline
    Period (s) & $4186.3285 \pm 0.0002$ \\
    PEPOCH (MJD) & $59965.03792 \pm 0.00003$ \\
    DM (pc/cm$^{-3}$) & $733 \pm 22$ \\
    $\tau_{\rm sc,1 GHz}$ (s) & ${\sim}0.07$ \\
    \hline
  \end{tabular}
\end{table}

@@

The measured DM of $733 \pm 22\,{\rm pc}\,{\rm cm}^{-3}$ is slightly higher than, but still consistent with, the in-band measurement of $710^{+200}_{-180}\,{\rm pc}\,{\rm cm}^{-3}$ given in \citetalias{2024MNRAS.535..909D}.
Because we have not attempted to simultaneously fit for both DM and scattering timescale, there will remain some small systematic error on this reported DM measurement.
Note, in particular, that the YMW16 and NE2001 models predict a slightly longer scattering time scale than the $70\,$ms that we have assumed throughout this work.
Breaking the degeneracy is possible in principle with a higher S/N average profile than what is achievable with the current data set.

@@

No significant linear or circular polarised emission was detected in the 2023 MeerKAT pulses.
This is likely due to low S/N coupled with the source not being centred in the beam.
Much more careful imaging analysis would be needed to obtain reliable measurements or limits on the polarised components of those pulses.
We also find no significant polarised emission from the ATCA pulses. \todo{[Akash: Can you please verify this?]}

@@

In contrast, the ATCA observation taken on 2025-10-12 did not yield any detections (out of four possible predicted ToAs that occurred during that observation).
This is despite the fact that pulses were detected with ATCA just eight days prior with a similar noise level, as well as the fact that pulses were detected at the MWA within 24 hours of the ATCA observation (none of the MWA observations were coincident with the ATCA observation).
However, there is enough pulse-to-pulse variability to allow for the possibility that the pulses during the 2025-10-12 were present, but fell below the detection threshold of ATCA.

@@

 This scientific work uses data obtained from Inyarrimanha Ilgari Bundara, the CSIRO Murchison Radio-astronomy Observatory. Support for the operation of the MWA is provided by the Australian Government (NCRIS), under a contract to Curtin University administered by Astronomy Australia Limited. ASVO has received funding from the Australian Commonwealth Government through the National eResearch Collaboration Tools and Resources (NeCTAR) Project, the Australian National Data Service (ANDS), and the National Collaborative Research Infrastructure Strategy.
% Skipped because it is acknowledged below.
% We acknowledge the Pawsey Supercomputing Centre which is supported by the Western Australian and Australian Governments.
% ASKAP -- I have fixed this to use the correct name for the observatory
The Australian SKA Pathfinder is part of the Australia Telescope National Facility which is managed by CSIRO (https://ror.org/05qajvd42). Operation of ASKAP is funded by the Australian Government with support from the National Collaborative Research Infrastructure Strategy. ASKAP and the MWA use the resources of the Pawsey Supercomputing Centre. Establishment of ASKAP, Inyarrimanha Ilgari Bundara, and the Pawsey Supercomputing Centre are initiatives of the Australian Government, with support from the Government of Western Australia and the Science and Industry Endowment Fund. We acknowledge the Wajarri Yamaji People as the Traditional Owners and Native Title Holders of the observatory site.

@@

It can be shown that pulses scatter-broadened by a thin screen\footnote{Relaxing the assumption of a single, thin, isotropic screen affects the shape of the scattered pulse in ways that could plausibly affect timing \citep{2009MNRAS.395.1391R}, but quantification of this is beyond the scope of this appendix.} will appear to the observer as the original pulse convolved with a one-sided exponential kernel with an associated timescale $\tau$ \citep{1972MNRAS.157...55W,1973MNRAS.163..345W}.
For intrinsically Gaussian pulses of scale $\sigma$, the result of this convolution is well described by the \textit{exponentially modified Gaussian} (EMG), as given in \Eqn~\ref{eqn:emg}.

@@

\begin{table*}
  \centering
  \caption{Times of arrival and other fitted pulse properties}
  \label{tbl:toas}
  \begin{tabular}{cccccc}
\hline
Telescope & Freq & ToA & $S_{\rm peak}$ & $\sigma$ & Fluence \\
 & (MHz) & (MJD) & (Jy) & (s) & (Jy\,s) \\
\hline
ASKAP & 888 & 59965.0429346(42) & 0.184(5) & 29.1(4) & 13.4(2) \\
MWA & 170 & 59966.061584(40) & 4(1) & 40(7) & 358(55) \\
ASKAP & 888 & 60040.913447(32) & 0.015(3) & 25(3) & 1.0(1) \\
MeerKAT & 1284 & 60092.8995476(100) & 0.0032(4) & 12.8(9) & 0.104(7) \\
MeerKAT & 1284 & 60092.947966(10) & 0.0033(6) & 12(1) & 0.10(1) \\
MeerKAT & 1284 & 60092.996466(11) & 0.0032(3) & 15.8(9) & 0.125(7) \\
MeerKAT & 1284 & 60093.044919(12) & 0.0030(3) & 16(1) & 0.122(7) \\
MWA & 200 & 60481.637466(65) & 0.8(4) & 24(8) & 50(11) \\
MWA & 200 & 60485.658977(33) & 0.7(2) & 16(4) & 29(3) \\
MWA & 200 & 60489.632266(20) & 1.4(3) & 14(2) & 48(3) \\
MWA & 200 & 60492.588020(24) & 2.4(6) & 14(3) & 87(7) \\
MWA & 200 & 60496.609639(18) & 1.5(3) & 17(2) & 67(4) \\
MWA & 200 & 60503.587085(14) & 2.0(2) & 17(2) & 82(3) \\
ASKAP & 888 & 60503.6347610(51) & 0.151(7) & 16.4(5) & 6.2(2) \\
MWA & 200 & 60506.542809(33) & 2(1) & 9(4) & 57(7) \\
MWA & 200 & 60510.564531(11) & 2.0(2) & 16(1) & 79(3) \\
MWA & 200 & 60519.528813(29) & 2.4(8) & 14(4) & 86(10) \\
MWA & 200 & 60522.533028(16) & 1.6(2) & 18(2) & 76(3) \\
MWA & 200 & 60527.524033(14) & 1.8(2) & 16(2) & 73(3) \\
MWA & 200 & 60530.528339(16) & 1.6(2) & 17(2) & 68(4) \\
MWA & 200 & 60537.506042(13) & 2.1(3) & 17(2) & 92(4) \\
MWA & 200 & 60541.479447(47) & 1.1(5) & 14(5) & 41(6) \\
MWA & 200 & 60544.483761(15) & 1.6(2) & 20(2) & 79(3) \\
MWA & 200 & 60551.461625(16) & 2.2(3) & 16(2) & 85(4) \\
MWA & 185 & 60572.395455(15) & 1.9(3) & 15(2) & 74(3) \\
MWA & 185 & 60572.443943(21) & 1.8(3) & 16(2) & 73(4) \\
MWA & 185 & 60572.540824(18) & 1.6(3) & 16(2) & 64(4) \\
MWA & 185 & 60572.589281(31) & 1.6(4) & 21(4) & 82(8) \\
ATCA & 2100 & 60587.270973(26) & 0.003(1) & 12(2) & 0.10(2) \\
ATCA & 2100 & 60587.319527(28) & 0.003(1) & 10(3) & 0.09(2) \\
MWA & 200 & 60592.456765(27) & 0.7(2) & 19(3) & 34(3) \\
MWA & 200 & 60592.505159(33) & 0.7(2) & 19(4) & 35(4) \\
MWA & 200 & 60593.474369(26) & 0.8(2) & 15(3) & 29(3) \\
MWA & 200 & 60593.522901(46) & 0.6(2) & 19(5) & 27(4) \\
MWA & 200 & 60594.443484(21) & 0.9(2) & 18(2) & 43(3) \\
MWA & 200 & 60594.491990(33) & 0.6(3) & 12(4) & 19(2) \\
MWA & 200 & 60595.461118(29) & 0.7(2) & 19(3) & 33(3) \\
MWA & 200 & 60595.509617(25) & 0.8(2) & 13(3) & 27(2) \\
MWA & 200 & 60596.430283(20) & 1.0(2) & 16(2) & 39(3) \\
MWA & 200 & 60596.478721(23) & 0.9(2) & 17(3) & 39(3) \\
MWA & 200 & 60597.447846(41) & 0.5(2) & 16(5) & 22(3) \\
MWA & 200 & 60597.496319(30) & 0.8(2) & 19(3) & 38(4) \\
MWA & 200 & 60599.434635(17) & 1.2(2) & 13(2) & 39(2) \\
MWA & 200 & 60599.483122(24) & 1.0(3) & 13(3) & 32(3) \\
MWA & 200 & 60600.500655(31) & 0.7(2) & 16(4) & 30(3) \\
MWA & 200 & 60602.438964(32) & 0.7(2) & 21(4) & 36(4) \\
MWA & 200 & 60602.487394(27) & 0.8(2) & 20(3) & 39(3) \\
MeerKAT & 813 & 60602.5835733(40) & 0.044(2) & 14.9(4) & 1.64(4) \\
\hline
  \end{tabular}
\end{table*}
